---
title: "My package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{My package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Fatality Analysis Reporting System (FARS)

The package includes differents function in order to show accidents in the US. Next, you will be able to see a summary for each function.

## 'fars_read' function

The function has like an input a filename character from 'make_filename' function. It is neccesary the file with data about the FARS in the US, then the function can read it and convert in a data frame.

## 'make_filename function

The function create the filename.

## 'fars_read_years' function

The function take both function 'make_filename' and 'fars_read_years' to create a single data frame or a list.

## 'fars_summarize_years' function

The function show summarize years. 

## 'fars_map_state function 

The function plot a graph with points that represents accidents for a specific state of US during a given year.

```{r setup}
fars_map_state(state.num = 45 , year = 2013)
```
